---
title: "Penguin Report"
author: ""
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  officedown::rdocx_document:
    reference_docx: template.docx
params:
  data: NULL
  xaxis: NULL
  yaxis: NULL
  groupvar: NULL
  prettynames: NULL
  tablelayout: NULL
  q1: NULL
  q2: NULL
  q3: NULL
  key: NULL
  flextab: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval=TRUE, message=FALSE, warning=FALSE)

library(dplyr)
library(tidyr)
library(ggplot2)
library(flextable)
library(officedown)
theme_set(theme_minimal())

correct1 <- if(params$q1 == params$key[[1]]) {"correct"} else {"incorrect"}
correct2 <- if(params$q2 == params$key[[2]]) {"correct"} else {"incorrect"}
correct3 <- if(params$q3 == params$key[[3]]) {"correct"} else {"incorrect"}

score <- sum(c(correct1, correct2, correct3) == "correct")

correct_fp <- fp_text_lite(color = "#70AD47", bold = TRUE)
incorrect_fp <- fp_text_lite(color = "#C32900", bold = TRUE)

q1_fp <- if(correct1 == "correct") {
  ftext("correct", correct_fp)
} else {
    ftext("incorrect", incorrect_fp)
}

q2_fp <- if(correct2 == "correct") {
  ftext("correct", correct_fp)
} else {
    ftext("incorrect", incorrect_fp)
}

q3_fp <- if(correct3 == "correct") {
  ftext("correct", correct_fp)
} else {
    ftext("incorrect", incorrect_fp)
  }
                    
```


# Your Penguin Plot  

The scatterplot below shows the relationship between `r params$prettynames[2]` and `r params$prettynames[1]` for each `r params$prettynames[3]` observed in the ``penguins`` data frame. Linear fit lines have been included for each group, making it easier to see if the relationship is positive or negative, strong or weak.

```{r penguinplot}
# Get pretty names for labels/titles
ylab <- params$pretty_names[1]
xlab <- params$pretty_names[2]
grouplab <- params$pretty_names[3]

colors <- c("darkorange","purple","cyan4")

# Create plot
params$data %>%
  ggplot(aes_string(x = params$xaxis, y = params$yaxis)) +
  # Add scatter points
  geom_point(aes_string(colour = params$groupvar,
                        shape = params$groupvar),
             size = 3) +
  # Include fit line
  geom_smooth(aes_string(colour = params$groupvar), 
              method = "lm", se = FALSE) +
  scale_colour_manual(values = colors) +
  # Add pretty labels
  labs(x = xlab, y = ylab) +
  guides(colour = guide_legend(grouplab),
         shape = guide_legend(grouplab))


```

# Your Penguin Table

The table below shows the mean and standard deviation (SD) of `r params$prettynames[2]` and `r params$prettynames[1]` for each `r params$prettynames[3]` observed in the ``penguins`` data frame. In addition, the table also includes the number of penguins within each group.

```{r penguintable, include = FALSE}
# Summarize relevant values
params$data %>%
  group_by(.data[[params$groupvar]]) %>%
  summarize(
    cases = n(),
    xvar_mean = mean(.data[[params$xaxis]], na.rm = T),
    xvar_sd = sd(.data[[params$xaxis]], na.rm = T),
    yvar_mean = mean(.data[[params$yaxis]], na.rm = T),
    yvar_sd = sd(.data[[params$yaxis]], na.rm = T)
  ) %>%
  # Create Data Table
  DT::datatable(options = list(dom = 't'), # only show table
                rownames = FALSE, # don't include rownames
                container = params$tablelayout # use custom layout
  ) %>%
  # Round summary stats to 2 decimals
  DT::formatRound(c("xvar_mean", "xvar_sd", "yvar_mean", "yvar_sd"), 2)


```

```{r penguintable2}
params$flextab
```

# Your Quiz Results

Below, you'll find your overall quiz score, as well as an overview of your answers (and correct answers if you answered incorrectly) to the quiz questions.
`r run_linebreak()`

## Score: `r paste0(score, "/3")`

`r run_linebreak()`
**1. On what island were most penguins observed?**  
Your response was `r params$q1`, which is `r q1_fp`. `r if(correct1 == "incorrect") {paste0("The correct answer is ", params$key[[1]], ".")}`  
`r run_linebreak()`
**2. How many male penguins were observed?**  
Your response was `r params$q2`, which is `r q2_fp`. `r if(correct2 == "incorrect") {paste0("The correct answer is ", params$key[[2]], ".")}`  
`r run_linebreak()`
**3. What penguin species has the highest average body mass?**  
Your response was `r params$q3`, which is `r q3_fp`. `r if(correct3 == "incorrect") {paste0("The correct answer is ", params$key[[3]], ".")}`  

                         